---
title: "Area of the high seas that is fished"
output: html_notebook
---

```{r}
library(raster)
library(sf)
library(tidyverse)


HS_shp <- read_sf("../../../Google Drive - UCSB/shapefiles/high-seas/high_seas.shp")
ocean_shp <- read_sf("../../../Google Drive - UCSB/shapefiles/ocean/ne_10m_ocean.shp")

binned_ais_vms_high_seas_effort <- read_csv("saved_files/binned_ais_vms_high_seas_effort.csv") %>% 
  filter(year == 2016)

binned_ais_vms_high_seas_effort_01 <- read_csv("saved_files/binned_ais_vms_high_seas_effort_tenth_degree_resolution.csv") %>% 
  filter(year == 2016)

hs_area <- 230
```

## Simple approach

```{r}
estimate_area_fished <- function(d, res){
  
  d %>% 
    mutate(lon_bin_center = floor(lon_bin_center/res)*res + 0.5*res,
           lat_bin_center = floor(lat_bin_center/res)*res + 0.5*res) %>% 
    group_by(lat_bin_center, lon_bin_center) %>% 
    summarise(fishing_hours = sum(fishing_hours, na.rm = T)) %>% 
    ungroup() %>% 
    mutate(area = cos(NISTunits::NISTdegTOradian(lat_bin_center))*(111/(1/res))^2) %>% 
    filter(fishing_hours > 0) %>% 
    summarise(fished_area = sum(area)/10^6) %>% 
    pull(fished_area)
}

estimate_area_fished(binned_ais_vms_high_seas_effort_01,0.5)
```

The simplest approach is to estimate the area fished using the 0.5ยบ resolution. This yields that `r estimate_area_fished(binned_ais_vms_high_seas_effort_01,0.5)`
million sq km of the high seas are fished (`r estimate_area_fished(binned_ais_vms_high_seas_effort_01,0.5)/230` %). Increasing the resolution to 0.25ยบ degrees, reduces this area to `r estimate_area_fished(binned_ais_vms_high_seas_effort_01,0.25)` sq km (`r estimate_area_fished(binned_ais_vms_high_seas_effort_01,0.25)/230` %) and further decreasing the resolution to 0.1ยบ the fished area is reduced to `r estimate_area_fished(binned_ais_vms_high_seas_effort_01, 0.1)` million (`r estimate_area_fished(binned_ais_vms_high_seas_effort_01,0.1)/230` %).

## Equal area approach

```{r}
binned_ais_vms_high_seas_effort_05 <- binned_ais_vms_high_seas_effort %>% 
  filter(year == 2016) %>%
  group_by(lat_bin_center, lon_bin_center) %>% 
  summarise(fishing_hours = sum(fishing_hours, na.rm = T)) %>% 
  filter(fishing_hours > 0) %>% 
  ungroup()

grid_latlon <- expand.grid(lat = seq(min(binned_ais_vms_high_seas_effort_05$lat_bin_center),
                                    max(binned_ais_vms_high_seas_effort_05$lat_bin_center), 0.5), 
                           lon = seq(min(binned_ais_vms_high_seas_effort_05$lon_bin_center),
                                     max(binned_ais_vms_high_seas_effort_05$lon_bin_center), 0.5))

gridded_fishing = left_join(grid_latlon, binned_ais_vms_high_seas_effort_05, 
                            by = c('lat' = 'lat_bin_center', 'lon' = 'lon_bin_center'))

gridded_fishing$fishing_hours = ifelse(is.na(gridded_fishing$fishing_hours), 0, gridded_fishing$fishing_hours)

sp::coordinates(gridded_fishing) = ~lon+lat

sp::proj4string(gridded_fishing) = sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs") 

#ensure fishing in on regular grid
sp::gridded(gridded_fishing) = TRUE
```

```{r}
fishing_raster_05 = raster::rasterFromXYZ(gridded_fishing, 
                                          crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

bb = extent(-180, 180, -78.5, 77)

fishing_raster_05 = setExtent(fishing_raster_05, bb, keepres = TRUE)
#this is Gall-Peters Equal Area Projection
fishing_raster_05 = projectRaster(fishing_raster_05, crs = "+proj=cea +lon_0=0 +x_0=0 +y_0=0 +lat_ts=45 +datum=WGS84 +units=m +no_defs", over = TRUE) 

fishing_raster_05[fishing_raster_05[] > 0] <- 1 
fishing_raster_05[fishing_raster_05[] <= 0] <- NA 

plot(fishing_raster_05)
```

```{r}
(hs_fished_area <- sum(fishing_raster_05[] >= 0, na.rm = T)*xres(fishing_raster_05)*yres(fishing_raster_05)/(10^6)/(10^6))

hs_fished_area/hs_area
```

### With 0.25 resolution

```{r}
binned_ais_vms_high_seas_effort_025 <- binned_ais_vms_high_seas_effort_01 %>% 
  mutate(lon_bin_center = floor(lon_bin_center/0.25)*0.25 + 0.5*0.25,
         lat_bin_center = floor(lat_bin_center/0.25)*0.25 + 0.5*0.25) %>% 
  group_by(lat_bin_center, lon_bin_center) %>% 
  summarise(fishing_hours = sum(fishing_hours, na.rm = T)) %>% 
  ungroup() %>% 
  filter(fishing_hours > 0)

grid_latlon <- expand.grid(lat = seq(min(binned_ais_vms_high_seas_effort_025$lat_bin_center),
                                    max(binned_ais_vms_high_seas_effort_025$lat_bin_center), 0.25), 
                           lon = seq(min(binned_ais_vms_high_seas_effort_025$lon_bin_center),
                                     max(binned_ais_vms_high_seas_effort_025$lon_bin_center), 0.25))

gridded_fishing = left_join(grid_latlon, binned_ais_vms_high_seas_effort_025, 
                            by = c('lat' = 'lat_bin_center', 'lon' = 'lon_bin_center'))

gridded_fishing$fishing_hours = ifelse(is.na(gridded_fishing$fishing_hours), 0, gridded_fishing$fishing_hours)

sp::coordinates(gridded_fishing) = ~lon+lat

sp::proj4string(gridded_fishing) = sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs") 

#ensure fishing in on regular grid
sp::gridded(gridded_fishing) = TRUE
```

```{r}
fishing_raster_025 = raster::rasterFromXYZ(gridded_fishing, 
                                          crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

bb = extent(-180, 180, -78.25, 77)

fishing_raster_025 = setExtent(fishing_raster_025, bb, keepres = TRUE)
#this is Gall-Peters Equal Area Projection
fishing_raster_025 = projectRaster(fishing_raster_025, crs = "+proj=cea +lon_0=0 +x_0=0 +y_0=0 +lat_ts=45 +datum=WGS84 +units=m +no_defs", over = TRUE) 

fishing_raster_025[fishing_raster_025[] > 0] <- 1 
fishing_raster_025[fishing_raster_025[] <= 0] <- NA 

plot(fishing_raster_025)
```

```{r}
(hs_fished_area <- sum(fishing_raster_025[] >= 0, na.rm = T)*xres(fishing_raster_025)*yres(fishing_raster_025)/(10^6)/(10^6))

<- <- hs_fished_area/hs_area
```
