---
title: 'High Seas Revenue from Sea Around Us and Reg Watson '
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '6'
---

```{r setup, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(plotly)
library(tidyverse)
library(bigrquery)
library(DBI)
library(forcats)
library(knitr)
library(sf)

BQ_connection <-  dbConnect(dbi_driver(), dataset = "", project = "world-fishing-827")

source("../general_project_files/effort_mapping_functions.R")
source("../general_project_files/gfw_themes.R")
source("../general_project_files/functions.R")

options(scipen = 999)

world_map <- rnaturalearth::ne_coastline(scale = 'small', returnclass = c("sf"))

max_lat = 90
min_lat = -90
max_lon = 180
min_lon = -180
cell_size  = 0.5
one_over_cellsize = 2
```


# Sea Around Us 

First we need to load and clean up the names in the database and fix many many errors. 

```{r load_revenue_by_country}
sau_data <- read_csv("source_info/updated_SAU_revenue/HighSeas_2014_Oct12.csv", 
                     col_types =  cols(catch_sum = col_number(),
                                       landed_value = col_number(),
                                       year = col_number()), 
                     n_max = Inf,
                     progress = FALSE)

effort_by_fao <- read_csv("../effort_and_coverage/saved_files/effort_by_high_seas_vessels_by_FAO_region.csv")
```

```{r}
country_lookup_table <- data_frame(fishing_entity = unique(sau_data$fishing_entity))

country_lookup_table$iso3 <- countrycode::countrycode(country_lookup_table$fishing_entity,  "country.name", "iso3c")

country_lookup_table$iso3[country_lookup_table$fishing_entity == "New Caledonia (France)"] <- "NCL"
country_lookup_table$iso3[country_lookup_table$fishing_entity == "Faeroe Isl. (Denmark)"] <- "FRO"
country_lookup_table$iso3[country_lookup_table$fishing_entity %in% c("Guam (USA)", "North Marianas (USA)")] <- "USA"
country_lookup_table$iso3[country_lookup_table$fishing_entity == "Réunion (France)"] <- "REU"
country_lookup_table$iso3[country_lookup_table$fishing_entity == "Micronesia"] <- "FSM"
country_lookup_table$iso3[country_lookup_table$fishing_entity == "Saint Pierre & Miquelon (France)"] <- "SPM"
country_lookup_table$iso3[country_lookup_table$fishing_entity == "Tokelau (New Zealand)"] <- "NZL"
```

```{r}
binned_high_seas_effort <- read_csv("../effort_and_coverage/saved_files/binned_high_seas_effort.csv")

binned_indo_high_seas_effort <-read_csv("../effort_and_coverage/saved_files/binned_indo_vms_high_seas_effort.csv")

effort_by_Indo_high_seas_vessels <- read_csv("../effort_and_coverage/saved_files/effort_by_Indo_high_seas_vessels.csv")

effort_by_Indo_high_seas_vessels_by_FAO_region <- read_csv("../effort_and_coverage/saved_files/effort_by_Indo_high_seas_vessels_by_FAO_region.csv")

binned_ais_vms_high_seas_effort <- bind_rows(binned_high_seas_effort %>% 
  select(year, lon_bin_center, lat_bin_center, FAO_region , flag_country_name, flag_iso3, sovereign_flag_country_name, sovereign_flag_iso3, gear_type , sub_gear_type , hours, fishing_hours, KW_hours, fishing_KW_hours),
binned_indo_high_seas_effort %>% 
   mutate(flag_country_name = "Indonesia",
                   flag_iso3 = "IDN",
                   sovereign_flag_country_name = flag_country_name,
                   sovereign_flag_iso3 = flag_iso3) %>% 
  left_join(effort_by_Indo_high_seas_vessels %>% 
              distinct(raw_registered_gear_type, gfw_gear, gfw_sub_gear)) %>% 
  select(year, lon_bin_center, lat_bin_center,FAO_region = FAO_Region, flag_country_name, flag_iso3, sovereign_flag_country_name, sovereign_flag_iso3, gear_type = gfw_gear, sub_gear_type = gfw_sub_gear, hours, fishing_hours, KW_hours, fishing_KW_hours))
```

```{r}
high_seas_gfw_countries <- binned_ais_vms_high_seas_effort %>% 
  filter(!(sovereign_flag_country_name == "Spain" & flag_country_name != "Spain")) %>% 
  filter(!(sovereign_flag_country_name == "Taiwan" & flag_country_name != "Taiwan")) %>% 
  distinct(flag_iso3, flag_country_name, sovereign_flag_iso3, sovereign_flag_country_name)
```

```{sql, connection = BQ_connection , output.var = "all_gfw_countries"}
SELECT
  flag_country_name,
  flag_iso3,
  sovereign_flag_country_name,
  sovereign_flag_iso3
FROM
  [high-seas:vessel_characteristics.complete_ais_vessel_characteristics]
GROUP BY
  flag_country_name,
  flag_iso3,
  sovereign_flag_country_name,
  sovereign_flag_iso3
```

```{r}
all_gfw_countries <- all_gfw_countries %>% 
  filter(!(sovereign_flag_country_name == "Spain" & flag_country_name != "Spain")) %>% 
  filter(!(sovereign_flag_country_name == "Taiwan" & flag_country_name != "Taiwan")) 
```

Match to high seas GFW countries

```{r}
country_lookup_table <- country_lookup_table %>% 
  left_join(high_seas_gfw_countries %>% 
              rename(iso3 = flag_iso3)
            ) 
```

Match to all countries

```{r}
country_lookup_table <- country_lookup_table %>% 
  left_join(all_gfw_countries %>% 
              select(iso3 = flag_iso3, country_name = flag_country_name)) %>% 
  mutate(flag_country_name = ifelse(is.na(flag_country_name), country_name, flag_country_name)) %>% 
  select(-country_name) %>% 
  mutate(sovereign_flag_country_name = ifelse(is.na(sovereign_flag_country_name),flag_country_name,sovereign_flag_country_name ),
         sovereign_flag_iso3 = ifelse(is.na(sovereign_flag_iso3),iso3,sovereign_flag_iso3)) %>% 
  mutate(sovereign_flag_country_name = ifelse(is.na(sovereign_flag_country_name),fishing_entity, sovereign_flag_country_name ),
         flag_country_name = ifelse(is.na(flag_country_name),fishing_entity,flag_country_name)) 

sau_data <- sau_data %>% 
  left_join(country_lookup_table)

fao_id_lookup <- read_tsv("source_info/fao_id_lookup.txt") 

sau_data <- sau_data %>% 
  rename(FAO_Region = fao_area) %>% 
  left_join(fao_id_lookup) %>% 
  select(year, fishing_entity, flag_country_name, flag_iso3 = iso3, sovereign_flag_country_name, sovereign_flag_iso3, FAO_Region,fao_area_name, lat_bin_center = lat,  lon_bin_center = lon , everything())
```

In total, SAU reports `r sum(sau_data$landed_value)/1000000000` billion dollars in revenue from fishing in the high seas in 2014. The following are the top countries in their database:

```{r}
sau_data %>%
  group_by(sovereign_flag_country_name) %>% 
  summarize(revenue = round(sum(landed_value)/1000000,2),
            catch = round(sum(catch)/1000,2)) %>% 
  mutate(percent = round(100*revenue/sum(revenue),2)) %>% 
  arrange(desc(revenue)) %>% 
  ungroup()
```

## SAU corrections

### Indonesia

We know Indonesia does not fish in regions other than 57

```{r}
sau_data <- sau_data %>% 
  filter(!(sovereign_flag_iso3 == "IDN" & !FAO_Region %in% c(51,57)))
```

### China

We know that currently SAU underestimates China's Squid jiggers catch on the high seas FAO 87 by half (they allocate to inside Peru's EEZ). They are missing about 180 million $ and 161 thousand tons of squid. 

```{r}
sau_data <- sau_data %>% 
  mutate(catch = ifelse(FAO_Region == 87 & scientific_name == "Dosidicus gigas" & sovereign_flag_iso3 == "CHN", catch/0.507, catch),
         landed_value = ifelse(FAO_Region == 87 & scientific_name == "Dosidicus gigas" & sovereign_flag_iso3 == "CHN", landed_value/0.442, landed_value))
```

Similarly, China's Squid jiggers landings on the high seas FAO 41 are underestimated. They report 356 M but the official number is 392 M. 

```{r}
sau_data <- sau_data %>% 
  mutate(landed_value = ifelse(FAO_Region == 41 & scientific_name == "Illex argentinus" & sovereign_flag_iso3 == "CHN", landed_value/0.905, landed_value))
```

Similarly, we can use the official SPRFMO estimates of squid catch for Taiwan and South Korea to validate SAU. We find that SAU underestimates catch by both countries by `r round(100*(1-sum(filter(sau_data,FAO_Region == 87, fishing_entity == "Taiwan", stringr::str_detect(scientific_name,"Dosidicus"))$catch)/4795))` and `r round(100*(1-sum(filter(sau_data,FAO_Region == 87, fishing_entity == "Korea (South)", stringr::str_detect(scientific_name,"Dosidicus"))$catch)/7203))` % for Taiwan and South Korea respectively.

```{r}
sau_data <- sau_data %>%
  mutate(
    catch = case_when(
      FAO_Region == 87 & scientific_name == "Dosidicus gigas" & sovereign_flag_iso3 == "KOR" ~ catch/0.815,
      FAO_Region == 87 & scientific_name == "Dosidicus gigas" & sovereign_flag_iso3 == "TWN" ~ catch/0.91,
      TRUE ~ catch
    ),
    landed_value = case_when(
      FAO_Region == 87 & scientific_name == "Dosidicus gigas" & sovereign_flag_iso3 == "KOR" ~ landed_value/0.815,
      FAO_Region == 87 & scientific_name == "Dosidicus gigas" & sovereign_flag_iso3 == "TWN" ~ landed_value/0.91,
      TRUE ~ landed_value
    )
  )
```

### Chile

We also know that SAU overestimates Chile's catch dramatically. Official report to the SPRFMO is 3983 tons, while SAU reports `r sum(filter(sau_data, sovereign_flag_iso3 == "CHL", FAO_Region == 87)$catch)`. The official number is only `r 3983/sum(filter(sau_data, sovereign_flag_iso3 == "CHL", FAO_Region == 87)$catch)` % of SAU. So we downscale accordingly. 

```{r}
sau_data <- sau_data %>% 
  mutate(catch = ifelse(FAO_Region == 87 & sovereign_flag_iso3 == "CHL", catch*0.012, catch),
         landed_value = ifelse(FAO_Region == 87 & sovereign_flag_iso3 == "CHL", landed_value*0.012, landed_value))
```

### Sri Lanka

Similarly, SAU overestimates Sri Lanka's high seas catch by 4x. The country's report to the IOTC suggest that catch was 31276 tons. SAU estimates `r sum(filter(sau_data, sovereign_flag_iso3 == "LKA")$catch)`. The official estimate is `r 100*31276/sum(filter(sau_data, sovereign_flag_iso3 == "LKA")$catch)` % so we need to downscale accordingly.


```{r}
sau_data <- sau_data %>% 
  mutate(catch = ifelse(sovereign_flag_iso3 == "LKA", catch*0.25, catch),
         landed_value = ifelse(sovereign_flag_iso3 == "LKA", landed_value*0.25, landed_value))
```

### India

India's high seas catch is also being overestimated. The country's official report to the IOTC states 7000 tons of tuna caught outside the EEZ, while SAU reports `r sum(filter(sau_data, sovereign_flag_iso3 == "IND")$catch)` tons. The official estimate is `r 100*7000/sum(filter(sau_data, sovereign_flag_iso3 == "IND")$catch)` % so we need to downscale accordingly.

```{r}
sau_data <- sau_data %>% 
  mutate(catch = ifelse(sovereign_flag_iso3 == "IND", catch*0.042, catch),
         landed_value = ifelse(sovereign_flag_iso3 == "IND", landed_value*0.042, landed_value))
```

### Russia

Finally, turns out SAU dramatically underestimates Russian catch on the North East Atlantic. According to the aggregated catch statistics of the [North East Atlantic Fisheries Commision ](https://www.neafc.org/system/files/Aggregated-catch-statistics-2014-final.pdf), Russia caught 185000 tons in the regulatory area. SAU reports `r sum(filter(sau_data, sovereign_flag_iso3 == "RUS", FAO_Region == 27)$catch)` which is only `r (100*sum(filter(sau_data, sovereign_flag_iso3 == "RUS", FAO_Region == 27)$catch)/185000)` % of the reported catch!

Using SAU prices of the species reported in the official NEAFC report, we estimate the revenue to be 148.31 million. SAU has `r sum(filter(sau_data, sovereign_flag_iso3 == "RUS", FAO_Region == 27)$landed_value)/10^6`.  This means we need to scale up revenue 

```{r}
 sau_data <- sau_data %>% 
   mutate(catch = ifelse(sovereign_flag_iso3 == "RUS" & FAO_Region == 27, catch/0.107, catch),
          landed_value = ifelse(sovereign_flag_iso3 == "RUS" & FAO_Region == 27 , landed_value/0.218, landed_value))
```

### Lithuania and Estonia

SAU dropped some HS catch of Lithuania and Estonia in FAO 27.  For Lithuania, SAU has only 0.08 million and is missing $2,756,870.  

```{r}
sau_data %>% 
  ungroup() %>%  
  filter(flag_iso3 %in% c("LTU")) %>% 
  group_by(flag_iso3, FAO_Region) %>% 
  summarize(revenue = round(sum(landed_value)/1000000,2),
            catch = sum(catch))
```

```{r}
sau_data <- sau_data %>% 
   mutate(catch = ifelse(sovereign_flag_iso3 == "LTU" & FAO_Region == 27, catch/0.009, catch),
          landed_value = ifelse(sovereign_flag_iso3 == "LTU" & FAO_Region == 27 , landed_value/0.028, landed_value))
```

And for Estonia, SAU does not have anything in region 27. Thus, we just add the missing catch and revenue to a random pixel in the region. Since we are not using SAU 0.5º data, this does not matter. 

```{r}
sau_data %>% 
  ungroup() %>%  
  filter(flag_iso3 %in% c("EST")) %>% 
  group_by(flag_iso3, FAO_Region) %>% 
  summarize(revenue = round(sum(landed_value)/1000000,2),
            catch = sum(catch))
```

```{r}
add_EST <- sau_data %>% 
  filter(flag_iso3 %in% c("EST")) %>% 
  head(1)

add_EST$FAO_Region <- 27
add_EST$fao_area_name <- "Atlantic, Northeast"
add_EST$lat_bin_center <- 55.75
add_EST$lon_bin_center <- -16.75
add_EST$scientific_name <- "Unknown"
add_EST$catch <- 5730
add_EST$landed_value <- 9106880

sau_data <- bind_rows(sau_data, add_EST)
```

### Crabs in FAO region 27

Catch of crabs is missing in FAO region 27 

```{r}
missing_crabs <- read_csv("source_info/updated_SAU_revenue/FAO27_HS_Crabs.csv") %>% 
  filter(Year == 2014) %>% 
  select(fishing_entity = `Fishing Country`, missing_catch = `HS Catch`, misssing_landed_value = `Landed Value`) %>% 
  group_by(fishing_entity) %>% 
  summarise(missing_catch = sum(missing_catch),
            misssing_landed_value = sum(misssing_landed_value))
```

```{r}
(crab_scale <- sau_data %>% 
  ungroup() %>%  
  filter(flag_iso3 %in% c("LTU", "RUS","NOR","LVA"), FAO_Region == 27) %>% 
  group_by(flag_iso3, FAO_Region) %>% 
  summarize(landed_value = sum(landed_value),
            catch = sum(catch)) %>% 
  left_join(missing_crabs %>% 
              mutate(flag_iso3 = countrycode::countrycode(fishing_entity, "country.name", "iso3c")),
            by = "flag_iso3") %>% 
  mutate(f_catch = catch/(catch + missing_catch),
         f_landed_value = landed_value/(landed_value + misssing_landed_value)) %>% 
  select(flag_iso3,FAO_Region, f_catch, f_landed_value) %>% 
  mutate_if(is.numeric, round, 3))
```

```{r}
sau_data <- sau_data %>% 
   mutate(catch = case_when(
     sovereign_flag_iso3 == "LTU" & FAO_Region == 27 ~ catch/0.735,
     sovereign_flag_iso3 == "NOR" & FAO_Region == 27 ~ catch/0.990,
     sovereign_flag_iso3 == "RUS" & FAO_Region == 27 ~ catch/0.994,
     TRUE ~ catch),
     landed_value = case_when(
     sovereign_flag_iso3 == "LTU" & FAO_Region == 27 ~ landed_value/0.5,
     sovereign_flag_iso3 == "NOR" & FAO_Region == 27 ~ landed_value/0.725,
     sovereign_flag_iso3 == "RUS" & FAO_Region == 27 ~ landed_value/0.784,
     TRUE ~ landed_value)
     )
```

After these adjustments, total high seas catch and landed value are:

```{r}
sau_data %>% 
  summarize(revenue = round(sum(landed_value, na.rm = T)/1000000,2),
            catch = sum(catch, na.rm = T))
```

```{r}
(summary_revenue_by_country <- sau_data %>% 
  filter(!is.na(sovereign_flag_iso3)) %>% 
   group_by(sovereign_flag_country_name, sovereign_flag_iso3) %>% 
   summarize(revenue = round(sum(landed_value)/1000000,2),
            catch = round(sum(catch)/1000,2)) %>%
   ungroup() %>% 
   mutate(percent = round(100*revenue/sum(revenue),2)) %>% 
   arrange(desc(revenue)) %>% 
   ungroup() %>% 
   mutate())
```

```{r}
(revenue_by_country.plot <- summary_revenue_by_country %>% 
  top_n(10, revenue) %>% 
  filter(!is.na(sovereign_flag_country_name)) %>% 
  ggplot(aes(x = forcats::fct_reorder(sovereign_flag_country_name, revenue), y = revenue, fill = desc(revenue))) +
  geom_bar(stat = "identity") +
  guides(fill = FALSE) +
  coord_flip() +
  theme_minimal() +
  theme(axis.title.x = element_text(margin = margin(10,0,0,0))) +
  labs(x = "", y = "Revenue (million usd)") +
  hrbrthemes::theme_ipsum()+
  geom_text(data = summary_revenue_by_country %>% 
              top_n(6, revenue), 
            aes(x =  forcats::fct_reorder(sovereign_flag_country_name, revenue),
                y = revenue, 
                label = paste(round(percent),"%",sep = "")),
            position = position_dodge(1), 
            hjust = -.1,
            size = 2) +
  ggsci::scale_fill_material("deep-purple", reverse = T)+
  theme(axis.text.x   = element_text(size = 8),
        axis.text.y   = element_text(size = 8)))
```

Aditionally, we can explore what's the most productive FAO region...

```{r}
sau_data %>%
  filter(!is.na(sovereign_flag_iso3)) %>% 
  group_by(FAO_Region, fao_area_name) %>% 
  summarize(revenue = sum(landed_value)/1000000) %>% 
  arrange(desc(revenue)) %>% 
  ungroup() %>% 
  mutate(percent = 100*revenue/sum(revenue)) %>% 
  ungroup() %>% 
  slice(1:10)
```

... and by country within FAO region: 

```{r revenue_by_region}
(summary_revenue_by_country_and_FAO <- sau_data %>%
   filter(!is.na(sovereign_flag_iso3)) %>% 
  group_by(sovereign_flag_iso3,  FAO_Region, fao_area_name) %>% 
  summarize(revenue = sum(landed_value)/1000000) %>% 
  arrange(desc(revenue)) %>% 
  ungroup() %>% 
  mutate(percent = 100*revenue/sum(revenue)))
```

```{r}
(revenue_by_country_and_FAO.plot <- summary_revenue_by_country_and_FAO %>% 
  top_n(20, revenue) %>% 
  filter(!is.na(sovereign_flag_iso3)) %>% 
  unite(fleet, sovereign_flag_iso3, FAO_Region) %>% 
  mutate(fleet = stringr::str_replace_all(fleet, "_"," ")) %>% 
  ggplot(aes(x = forcats::fct_reorder(fleet, revenue), y = revenue, fill = desc(revenue))) +
  geom_bar(stat = "identity") +
  guides(fill = FALSE) +
  coord_flip() +
  theme_minimal() +
  theme(axis.title.x = element_text(margin = margin(10,0,0,0))) +
  labs(x = "", y = "Revenue (million usd)") +
  hrbrthemes::theme_ipsum()+
  geom_text(data = summary_revenue_by_country_and_FAO %>% 
              top_n(5, revenue) %>% 
              filter(!is.na(sovereign_flag_iso3)) %>% 
              unite(fleet, sovereign_flag_iso3, FAO_Region) %>% 
              mutate(fleet = stringr::str_replace_all(fleet, "_"," ")) , 
            aes(x =  forcats::fct_reorder(fleet, revenue),
                y = revenue, 
                label = paste(round(percent),"%",sep = "")),
            position = position_dodge(1), 
            hjust = -.1,
            size = 2) +
  ggsci::scale_fill_material("green", reverse = T)+
  theme(axis.text.x   = element_text(size = 8),
        axis.text.y   = element_text(size = 8)))

write_csv(sau_data, "saved_files/processed_sau_data_2014.csv")
```

```{r}
sau_data <- read_csv("saved_files/processed_sau_data_2014.csv") %>% 
    filter(!is.na(sovereign_flag_iso3))
```

## Matching at Flag and  FAO region level

### All catch but Squid

```{r}
high_seas_effort_by_flag_and_FAO_region <- bind_rows(
  effort_by_fao %>%
    filter(!(sovereign_flag_iso3 %in% c("CHN") & gear_type == "squid_jigger") |
             (sovereign_flag_iso3 %in% c("CHN") & is.na(gear_type))) %>%
  filter(!(sovereign_flag_iso3 %in% c("KOR", "TWN") &
           gear_type == "squid_jigger" &
           FAO_region %in% c(41,87)) |
           (sovereign_flag_iso3 %in% c("KOR", "TWN") & is.na(gear_type))) %>% 
    group_by(year, sovereign_flag_iso3, FAO_region) %>%
    summarise(fishing_KW_hours_hs = sum(fishing_KW_hours_hs, na.rm = T),
              fishing_KW_days_hs = sum(fishing_KW_days_hs, na.rm = T)),
  effort_by_Indo_high_seas_vessels_by_FAO_region %>%
    group_by(year, FAO_region) %>%
    summarise(fishing_KW_hours_hs = sum(fishing_KW_hours_hs,  na.rm = T),
              fishing_KW_days_hs = sum(fishing_KW_days_hs, na.rm = T)) %>%
    mutate(sovereign_flag_iso3 = "IDN") %>%
    select(year, sovereign_flag_iso3, everything())
) %>%
  filter(!is.na(FAO_region), fishing_KW_hours_hs > 0)

high_seas_effort_by_flag_and_FAO_region <- high_seas_effort_by_flag_and_FAO_region %>% 
  replace_na(list(sovereign_flag_iso3 = "UNK"))
```

```{r}
matched_revenue_at_fao_level_all_years <- sau_data %>%
  filter(!(sovereign_flag_iso3 %in% c("CHN") & 
             (stringr::str_detect(scientific_name,"Dosidicus") |
                stringr::str_detect(scientific_name,"Illex") |
                 stringr::str_detect(scientific_name,"Teuthida")))) %>% 
  filter(!(sovereign_flag_iso3 %in% c("TWN", "KOR") & FAO_Region %in% c(41,87) &
             (stringr::str_detect(scientific_name,"Dosidicus") |
                stringr::str_detect(scientific_name,"Illex") |
                 stringr::str_detect(scientific_name,"Teuthida")))) %>% 
  rename(FAO_region = FAO_Region) %>% 
  group_by(FAO_region, sovereign_flag_iso3) %>%
  summarize(revenue = sum(landed_value),
            catch = sum(catch)) %>% 
  ungroup() %>% 
  left_join(high_seas_effort_by_flag_and_FAO_region)

matched_revenue_at_fao_level_all_years %>%
  filter(year == 2016) %>% 
  #group_by(sovereign_flag_iso3) %>% 
  summarise(revenue = sum(revenue)/10^6) %>% 
  arrange(desc(revenue))
```


```{r}
matched_revenue_at_fao_level_all_years %>%
  mutate(revenue = round(revenue/10^6)) %>% 
  filter(year == 2016) %>% 
  arrange(desc(revenue))
```

### Squid for CHN, TWN, KOR

```{r}
matched_revenue_China_SJ <- sau_data %>%
  rename(FAO_region = FAO_Region) %>% 
  filter((sovereign_flag_iso3 %in% c("CHN") & (stringr::str_detect(scientific_name,"Dosidicus") |
           stringr::str_detect(scientific_name,"Illex") |
           stringr::str_detect(scientific_name,"Teuthida"))) |
           (sovereign_flag_iso3 %in% c("TWN","KOR") & FAO_region %in% c(41,87) & (stringr::str_detect(scientific_name,"Dosidicus") |
           stringr::str_detect(scientific_name,"Illex") |
           stringr::str_detect(scientific_name,"Teuthida")))) %>% 
  group_by(FAO_region, sovereign_flag_iso3) %>%
  summarize(revenue = sum(landed_value),
            catch = sum(catch)) %>% 
  ungroup() %>% 
  left_join(effort_by_fao %>% 
              filter((sovereign_flag_iso3 %in% c("CHN") & gear_type == "squid_jigger") |
                      (sovereign_flag_iso3 %in% c("TWN","KOR") & gear_type == "squid_jigger" & FAO_region %in% c(41,87)) ) %>% 
              group_by(year, sovereign_flag_iso3, FAO_region, gear_type) %>% 
              summarise(fishing_KW_hours_hs = sum(fishing_KW_hours_hs, na.rm = T),
                        fishing_KW_days_hs = sum(fishing_KW_days_hs, na.rm = T))) %>% 
  select(sovereign_flag_iso3, gear_type, everything())

matched_revenue_China_SJ %>% 
  filter(year == 2016) %>% 
  arrange(revenue)
```

```{r}
matched_revenue_China_SJ %>%
  filter(year == 2016) %>% 
  summarise(sum(revenue)/10^6)
```

### All catch matched with effort

```{r}
matched_revenue_at_fao_level_all_years %>% 
  filter(!is.na(year)) %>% 
  group_by(year) %>% 
  summarise(revenue_matched_with_fishing_KW_hours = sum(revenue[fishing_KW_hours_hs > 0 & !is.na(fishing_KW_hours_hs)])/10^6) %>% 
  left_join(matched_revenue_China_SJ %>% 
              filter(!is.na(year)) %>% 
              group_by(year) %>% 
              summarise(CHN_SJ_revenue_matched_with_fishing_KW_hours = sum(revenue[fishing_KW_hours_hs > 0 & !is.na(fishing_KW_hours_hs)])/10^6)) %>% 
              mutate(revenue_matched_with_fishing_KW_hours = revenue_matched_with_fishing_KW_hours + CHN_SJ_revenue_matched_with_fishing_KW_hours) %>% 
              select(-CHN_SJ_revenue_matched_with_fishing_KW_hours) %>% 
              mutate(fraction_revenue_matched_with_fishing_KW_hours = revenue_matched_with_fishing_KW_hours/(sum(sau_data$landed_value)/10^6))
```

```{r}
#write_csv(matched_revenue_at_fao_level_all_years, "saved_files/matched_revenue_at_fao_level_all_years.csv")
#write_csv(matched_revenue_China_SJ, "saved_files/matched_revenue_China_SJ.csv")
```

## What are the most productive regions/countries that we are able to match?

```{r}
(revenue_vs_fishing_energy_plot <- bind_rows(
  matched_revenue_at_fao_level_all_years %>%
    filter(year == 2016, fishing_KW_hours_hs > 1 & !is.na(fishing_KW_hours_hs)) %>%
    select(sovereign_flag_iso3, FAO_region, fishing_KW_hours_hs, revenue),
  matched_revenue_China_SJ %>%
    filter(year == 2016, fishing_KW_hours_hs > 1 & !is.na(fishing_KW_hours_hs)) %>%
    select(sovereign_flag_iso3, FAO_region, fishing_KW_hours_hs, revenue)
) %>%
  ggplot(aes(x = fishing_KW_hours_hs, y = revenue, col = factor(FAO_region), key = sovereign_flag_iso3)) +
  geom_point() +
  theme_minimal() +
  guides(
    stat = FALSE,
    col = guide_legend(
      title = "Fao Region",
      ncol = 3
    )
  ) +
  scale_y_log10() +
  scale_x_log10()
)
```

## Estimate Revenue Ratios

```{r}
revenue_ratios_by_country_and_fao <- matched_revenue_at_fao_level_all_years %>% 
  filter(!is.na(year), fishing_KW_hours_hs > 0 ) %>% 
  group_by(year, sovereign_flag_iso3, FAO_region) %>% 
  summarize(total_revenue = sum(revenue), 
            revenue_per_fishing_KWh = revenue/fishing_KW_hours_hs,
            revenue_per_fishing_KW_day = revenue/fishing_KW_days_hs,
            catch_per_fishing_KWh = catch/fishing_KW_hours_hs,
            catch_per_fishing_KW_day = catch/fishing_KW_days_hs) %>% 
  ungroup()
```

```{r}
revenue_ratios_China_SJ <- matched_revenue_China_SJ %>% 
  filter(!is.na(year),  fishing_KW_hours_hs > 0 ) %>% 
  group_by(year, sovereign_flag_iso3, gear_type , FAO_region) %>% 
  summarize(total_revenue = sum(revenue), 
            revenue_per_fishing_KWh = revenue/fishing_KW_hours_hs,
            revenue_per_fishing_KW_day = revenue/fishing_KW_days_hs,
            catch_per_fishing_KWh = catch/fishing_KW_hours_hs,
            catch_per_fishing_KW_day = catch/fishing_KW_days_hs) %>% 
  ungroup()
```

```{r}
revenue_ratios_by_country_and_fao %>% 
  filter(year == 2016) %>% 
  summarise(sum(total_revenue)/10^6)
```


```{r}
revenue_ratios_China_SJ %>% 
  filter(year == 2016) %>% 
  summarise(sum(total_revenue)/10^6)
```

Total matched revenue is 7655 millions.

```{r}
(revenue_per_kwh_barplot <- revenue_ratios_by_country_and_fao %>% 
  filter(year == 2016) %>% 
  unite(country_fao, sovereign_flag_iso3, FAO_region, remove = T) %>% 
  top_n(30, revenue_per_fishing_KWh) %>% 
  ggplot()+
  geom_bar(aes(x = forcats::fct_reorder(country_fao,revenue_per_fishing_KWh) , y = revenue_per_fishing_KWh), stat = "identity") +
  coord_flip()+
  ylab("thousand $ per KWh")+
  xlab("")+
  theme_minimal()+
  labs(title = "Revenue per Kwh by country and fao region"))
```


```{r eval = F}
BQ_connection <-  dbConnect(dbi_driver(), dataset = "revenue", project = "high-seas", billing = "world-fishing-827")

if(dbExistsTable(BQ_connection, "revenue_ratios_by_iso3_and_fao")){
  dbRemoveTable(BQ_connection, "revenue_ratios_by_iso3_and_fao") 
  dbWriteTable(BQ_connection, "revenue_ratios_by_iso3_and_fao", revenue_ratios_by_country_and_fao)
} else {dbWriteTable(BQ_connection, "revenue_ratios_by_iso3_and_fao", revenue_ratios_by_country_and_fao)}

if(dbExistsTable(BQ_connection, "revenue_ratios_China_SJ")){
  dbRemoveTable(BQ_connection, "revenue_ratios_China_SJ") 
  dbWriteTable(BQ_connection, "revenue_ratios_China_SJ", revenue_ratios_China_SJ)
} else {dbWriteTable(BQ_connection, "revenue_ratios_China_SJ", revenue_ratios_China_SJ)}
```

```{r}
revenue_ratios_by_country_and_fao %>% 
  write_csv("saved_files/revenue_ratios_by_flag_and_FAO.csv")

revenue_ratios_China_SJ %>% 
  write_csv("saved_files/revenue_ratios_China_SJ.csv")
```

```{r}
revenue_ratios_by_country_and_fao <- 
  read_csv("saved_files/revenue_ratios_by_flag_and_FAO.csv")

revenue_ratios_China_SJ<- 
  read_csv("saved_files/revenue_ratios_China_SJ.csv")

bind_rows(
  revenue_ratios_China_SJ %>%
    filter(year == 2016) %>%
    group_by(sovereign_flag_iso3) %>%
    summarise(r = sum(total_revenue)),
  revenue_ratios_by_country_and_fao %>%
    filter(year == 2016) %>%
    group_by(sovereign_flag_iso3) %>%
    summarise(r = sum(total_revenue))
) %>%
  group_by(sovereign_flag_iso3) %>%
  summarise(r = sum(r) / 10 ^ 6) %>%
  arrange(desc(r))
```

## Is catch correlated with effort?

```{r}
catch_by_flag_by_FAO <- bind_rows(matched_revenue_at_fao_level_all_years %>% 
  filter(year == 2016) %>% 
  group_by(sovereign_flag_iso3, FAO_region) %>% 
  summarize(catch = sum(catch)),
matched_revenue_China_SJ %>% 
  filter(year == 2016) %>% 
  group_by(sovereign_flag_iso3, FAO_region) %>% 
  summarize(catch = sum(catch)))

effort_and_catch_by_country_and_FAO <- catch_by_flag_by_FAO %>% 
  left_join(high_seas_effort_by_flag_and_FAO_region %>% 
              filter(year == 2016) %>% 
              select(sovereign_flag_iso3, FAO_region, fishing_KW_days_hs)) %>% 
  arrange(desc(catch))
```

```{r}
effort_and_catch_by_country_and_FAO <- effort_and_catch_by_country_and_FAO %>% 
  mutate(log_effort = log(fishing_KW_days_hs),
         log_catch = log(catch))

effort_catch_lm <- lm(log_catch ~ log_effort, data = effort_and_catch_by_country_and_FAO)

effort_catch_eq <- substitute(italic(ln(C)) == a  + b ~ italic(ln(E)), 
               list(a = format(coef(effort_catch_lm)[1], digits = 3), 
                    b = format(coef(effort_catch_lm)[2], digits = 3)))

effort_catch_eq <- as.character(as.expression(effort_catch_eq))

effort_catch_data <- modelr::add_predictions(effort_and_catch_by_country_and_FAO,
                                                 effort_catch_lm)
      
(R2 <- as.character(as.expression(paste("R^2 :",round(broom::glance(effort_catch_lm)$adj.r.squared,2)))))

(effort_catch_relationship <- effort_catch_data %>% 
  ggplot(aes(exp(log_effort), exp(log_catch)))+
  geom_point()+
  geom_line(aes(exp(log_effort), exp(pred)), col = "orange")+
  scale_y_log10(label = scales::comma)+
  scale_x_log10(label = scales::comma)+
  hrbrthemes::theme_ipsum()+
  annotate("text", x = 7000, y = 4000000, label = effort_catch_eq, parse = TRUE, col = 'Navy')+
  annotate("text", x = 1600, y = 1000000, label = R2, parse = TRUE, col = 'Navy') +
  labs(y = "Catch (tons)", x = "Effort (KW days)"))
```

